Classless Java

### 2015-11-10 paper/sections/Formalization.tex
revised method overriding mechanism description.

@@

Figure~\ref{fig:javabug} shows the method overriding mechanism in Java. In the
example, there are 6 interfaces \texttt{A1,A2,A3,B1,B2,B3} with methods all
named as \texttt{m} which are either abstract or default methods. If we define a
new interface \texttt{M} that extends two of these interfaces, then the method
overriding result is shown in the table. For example, row2 col2 means \texttt{M
  extends A1,B1}. The result is \texttt{ERROR} because the abstract method
\texttt{T m();} in \texttt{A1} conflicts with the method \texttt{default T m()
  {...}} in \texttt{B1}. Readers may also figure out other extending cases by
following this way of interpretation. The interesting case in row4 col2 where
\texttt{M extends A1,B3}, the result should be \texttt{ERROR}, however in Java
the experimental result is \texttt{B3.m}. Because if we think consistently, this
case is esencially a method conflicting situation with abstract methods and
default methods, which is no different than the first case.

>>>>

\subsection{Method Overriding Mechanism}
We summarize the mechanism for method overriding below (all methods considered
here are methods with the same name and argument types):

1. Two abstract methods with subtyping relation do not cause conflict, and the
most specific one wins. Subtyping relation for two methods means they have the
same arguments' types and one return type is a subtype of the other one. For
example:
\begin{lstlisting}
interface A1 { Object m(); }
interface B1 { Integer m();}
interface C1 extends A1,B1 {} //accepted
\end{lstlisting}
Method \texttt{Integer m()} in \texttt{B} wins over method \texttt{Object m()}
in \texttt{A} because \texttt{Integer <: Object}.

2. A default method conflict with another default method or abstract method. For
example:
\begin{lstlisting}
interface A2 { default int m() {return 1;}}
interface B2 { int m(); }
interface C2 { default int m() {return 2;}}
interface D2 extends A2,B2 {} //rejected due to conflicting methods
interface E2 extends A2,C2 {} //rejected due to conflicting methods
\end{lstlisting}

3. The method in the current interface wins over any methods defined in its
super-interfaces, provided that the method conform to the subtype of all methods
in its super-interfaces, i.e., the method is the most specific one. For example:
\begin{lstlisting}
interface D3 extends A2,B2 { int m(); } //accepted
interface E3 extends A2,C2 { int m(); } //accepted
\end{lstlisting}

@@

Figure~\ref{fig:javabug} shows the method overriding bug in Java. In the
example, there are 6 interfaces \texttt{A1,A2,A3,B1,B2,B3} with methods all
named as \texttt{m} which are either abstract or default methods. If we define a
new interface \texttt{M} that extends two of these interfaces, then the method
overriding result is shown in the table. For example, row2 col2 means \texttt{M
  extends A1,B1}. The result is \texttt{ERROR} because the abstract method
\texttt{T m();} in \texttt{A1} conflicts with the method \texttt{default T m()
  {...}} in \texttt{B1}. Readers may also figure out other extending cases by
following this way of interpretation. The interesting case in row4 col2 where
\texttt{M extends A1,B3}, the result should be \texttt{ERROR}, however in Java
the experimental result is \texttt{B3.m}. Because if we think consistently, this
case is esencially a method conflicting situation with abstract methods and
default methods, which is no different than the first case.
